Evolution of ORM Systems: Formal Foundations

### 2013-01-31 doc/description.tex
tables in case study

\begin{figure}
\begin{subfigure}[b]{0.5\textwidth}
	\includegraphics[width=\textwidth]{./images/case_app_1}
	\caption{The application model.}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
	\includegraphics[width=\textwidth]{./images/case_db_1}
	\caption{The database model.}
\end{subfigure}
	\caption{The initial state of the example used in the case study. There is a repetition of information structure in the $Person$ and $LegalPerson$ class.}
	\label{fig:case1}
\end{figure}

@@

\begin{figure}
\begin{subfigure}[b]{0.5\textwidth}
	\includegraphics[width=\textwidth]{./images/case_app_5}
	\caption{The application model.}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
	\includegraphics[width=\textwidth]{./images/case_db_5}
	\caption{The database model.}
\end{subfigure}
	\caption{The state of the software after the information are extracted into separated classes and associations are created.}
	\label{fig:case2}
\end{figure}
%Next two evolution steps are bit intuitive but necessary for the next evolution.  then the temporary class can be merged together and finally the temporary class has to be renamed to $Address$:
The two temporary classes can be merged together as they have the same structure. All associations pointing to one of the temporary classes are redirected to the newly created class.
\begin{align*}
%
%& \oplus AddAssociation("Person", \\
%& assoc("address", "Address\_tmp2", 1, 1), \varnothing) \\
%& \oplus AddAssociation("LegalPerson", \\
%& assoc("residentialAddress", "Address\_tmp1", 1, 1),\varnothing) \\
%
S_2 &= S_1 \oplus Merge("Address\_tmp1", "Address\_tmp2", "Address") \\
\end{align*}
Finally the associations are renamed and the evolution end.
\begin{align*}
S_3 &= S_2  \oplus RenameAssociation("Person", "Address\_tmp1", "Address")\\
& \oplus RenameAssociation("LegalPerson", "Address\_tmp2". "Address")\\
\end{align*}

\begin{figure}
\begin{subfigure}[b]{0.5\textwidth}
	\includegraphics[width=\textwidth]{./images/case_app_9}
	\caption{The application model.}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
	\includegraphics[width=\textwidth]{./images/case_db_8}
	\caption{The database model.}
\end{subfigure}
	\caption{The final state of the case study example. There is one class containing information about address for the whole software and data were migrated.}
\end{figure}

>>>>

\begin{figure}
\begin{subfigure}[b]{0.5\textwidth}
	\includegraphics[width=\textwidth]{./images/case_app_1}
	\caption{The application model.}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
	\includegraphics[width=\textwidth]{./images/case_db_1}
	\caption{The database model.}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\begin{tabular}{| c | l | l | l | l | }
	 	\hline
		Id &  Surname & Street & City & ZIP  \\ \hline  
		11 & Jackson & Central Park St & New York & 100 01  \\ \hline
		12 & Clooney & S Orange Ave & Orlando & 320 24  \\ \hline
	\end{tabular}
	\caption{Data stored in the table $Person$.}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\begin{tabular}{| c | l | l | l | l | c |}
	 	\hline
		Id &  BusinessName & Street & City & ZIP \\ \hline  
		100 & Tools \& Machines & Olive ave. & New York & 100 01 \\ \hline
		200 & AI Robotics & Pine ave. & LA & 900 03  \\ \hline
	\end{tabular}
	\caption{Data stored in the table $LegalPerson$.}
\end{subfigure}
	\caption{The initial state of the example used in the case study. There is a repetition of information structure in the $Person$ and $LegalPerson$ class.}
	\label{fig:case1}
\end{figure}

@@

\begin{figure}
\begin{subfigure}[b]{0.5\textwidth}
	\includegraphics[width=\textwidth]{./images/case_app_5}
	\caption{The application model.}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
	\includegraphics[width=\textwidth]{./images/case_db_5}
	\caption{The database model.}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\begin{tabular}{| c | l |}
	 	\hline
		Id &  Surname \\ \hline  
		11 & Jackson  \\ \hline
		12 & Clooney  \\ \hline
	\end{tabular}
	\caption{Data stored in the table $Person$.}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\begin{tabular}{| c | l | l | l | l |}
	 	\hline
		Id & Street & City & ZIP & Person \\ \hline  
		11 & Central Park St & New York & 100 01 & 11  \\ \hline
		12 & Orange Ave & Orlando & 320 24 & 12 \\ \hline
	\end{tabular}
	\caption{Data stored in the table $Address\_tmp1$.}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\begin{tabular}{| c | l |}
	 	\hline
		Id &  BusinessName  \\ \hline  
		100 & Tools \& Machines  \\ \hline
		200 & AI Robotics \\ \hline
	\end{tabular}
	\caption{Data stored in the table $LegalPerson$.}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\begin{tabular}{| c | l | l | l | l |}
	 	\hline
		Id & Street & City & ZIP & LegalPerson\\ \hline  
		100 & Olive ave. & New York & 100 01 & 100 \\ \hline
		200 & Pine ave. & LA & 900 03 & 200  \\ \hline
	\end{tabular}
	\caption{Data stored in the table $Address\_tmp2$.}
\end{subfigure}

	\caption{The state of the software after the information are extracted into separated classes and associations are created.}
	\label{fig:case2}
\end{figure}
%Next two evolution steps are bit intuitive but necessary for the next evolution.  then the temporary class can be merged together and finally the temporary class has to be renamed to $Address$:
The two temporary classes can be merged together as they have the same structure. All associations pointing to one of the temporary classes are redirected to the newly created class.
\begin{align*}
%
%& \oplus AddAssociation("Person", \\
%& assoc("address", "Address\_tmp2", 1, 1), \varnothing) \\
%& \oplus AddAssociation("LegalPerson", \\
%& assoc("residentialAddress", "Address\_tmp1", 1, 1),\varnothing) \\
%
S_2 &= S_1 \oplus Merge("Address\_tmp1", "Address\_tmp2", "Address") \\
\end{align*}
Finally the associations are renamed and the evolution end.
\begin{align*}
S_3 &= S_2  \oplus RenameAssociation("Person", "Address\_tmp1", "Address")\\
& \oplus RenameAssociation("LegalPerson", "Address\_tmp2". "Address")\\
\end{align*}

\begin{figure}
\begin{subfigure}[b]{0.5\textwidth}
	\includegraphics[width=\textwidth]{./images/case_app_9}
	\caption{The application model.}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
	\includegraphics[width=\textwidth]{./images/case_db_8}
	\caption{The database model.}
\end{subfigure}

\begin{subfigure}[b]{\textwidth}
	\centering
	\begin{tabular}{| c | l |}
	 	\hline
		Id &  Surname \\ \hline  
		11 & Jackson  \\ \hline
		12 & Clooney  \\ \hline
	\end{tabular}
	\caption{Data stored in the table $Person$.}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\begin{tabular}{| c | l |}
	 	\hline
		Id &  BusinessName  \\ \hline  
		100 & Tools \& Machines  \\ \hline
		200 & AI Robotics \\ \hline
	\end{tabular}
	\caption{Data stored in the table $LegalPerson$.}
\end{subfigure}
\begin{subfigure}[b]{\textwidth}
	\centering
	\begin{tabular}{| c | l | l | l | l | l |}
	 	\hline
		Id & Street & City & ZIP & Person & LegalPerson\\ \hline  
		1 & Olive ave. & New York & 100 01 & & 100 \\ \hline
		2 & Pine ave. & LA & 900 03 & & 200  \\ \hline
		3 & Central Park St & New York & 100 01 & 11 &  \\ \hline
		4 & Orange Ave & Orlando & 320 24 & 12 &\\ \hline
	\end{tabular}
	\caption{Data stored in the table $Address\_tmp2$.}
\end{subfigure}

	\caption{The final state of the case study example. There is one class containing information about address for the whole software and data were migrated.}
\end{figure}
